The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-06-19 razzo-methods.tex
Folded in a readable way
Improve methods

We can easily simulate such processes in continuous time using the Doob-Gillespie algorithm. Simulations are performed using the function "mbd\_sim" from the \verb;mbd; package (\citep{mbd}).
We let parameters vary using all possible combinations of value included in Table~\ref{tab:simulation_parameters} to simulate $1000$ independent trees for each parameter setting.

>>>>

We can easily simulate such processes in continuous time using the 
Doob-Gillespie algorithm. Simulations are performed using the 
function "mbd\_sim" from the \verb;mbd; package (\citep{mbd}).
We let parameters vary using all possible combinations of values
as shown in Table~\ref{tab:simulation_parameters}.
For each parameter setting, we simulate $1000$ independent trees.

We have picked the parameters in such a way that in the most speciose
setting, the simulated trees have usually less than 200 taxa.
